\chapter*{Acknowledgments}
\indent This report is the official document of the Master Thesis conducted for 30 ECTS by Vinayak Gholap in the course of M.Sc. Computational Engineering. \par
I would like to specially thank my advisor Dr.\,Jean-Paul Pelteret for providing me this interesting topic and for his continuous support, guidance and honest remarks during the course of this work. He has given me the freedom and time to work on my concepts and help me channelize our ideas into appropriate direction. I also thank my second supervisor Dr.\,Prashant Saxena for his valuable feedbacks on the documentation and his insightful suggestions to overcome the hurdles and difficulties that we faced in the course of this research. This project would have not been possible without the many fruitful discussions and conversations the three of us have had. \par  
I would like to thank Prof.\,Dr.-Ing.\,Paul Steinmann for providing the working environment at his chair. His insightful courses have been instrumental in my personal knowledge development over the past three years. \par 
I would like to sincerely express my gratitude to all the people who have helped me continuously through this exciting journey. A cheerful shout-out to Dr.\,Denis Davydov for introducing me to the \texttt{deal.II} library through a project opportunity which helped me with an easy start to my thesis. I would specially like to thank the \texttt{deal.II} community group and the contributors for the wonderful platform they have build to share and communicate the thoughts with other people. \par 
Above all, I would like to express my sincere gratitude to my family and my brother and sisters in India and my friends in Germany for their kind love and persistent belief in me throughout my studies. The moral support and love that I received from them has made this journey comfortable and worthwhile. \newline\par 

\noindent Vinayak Gholap \par 
\noindent Erlangen, \today
